Python as a machine learning language: experiences from the scikit-learn project

### 2013-06-12 paper.tex
batch processing

The public API is oriented toward batch processing
to enable efficient implementation.
While classification and regression algorithms
can make predictions for single samples,
and some algorithms in \sklearn can perform online learning
(e.g. stochastic gradient descent for linear SVMs and logistic regression,
an online variant of $k$-means based on \citealt{sculley2010web}),
these algorithm are really intended to be used on small batches of samples.
Doing so makes optimal use of NumPy and SciPy
because they prevent the overhead inherent in Python function calls
and the language's per-element dynamic type checking.

>>>>

The public API is oriented towards batch processing. While classification and
regression algorithms can make predictions for single samples, most \sklearn
algorithms are intended to be used on batches of data. For efficiency reasons,
this indeed makes the use of NumPy and SciPy optimal by preventing the overhead
inherent to Python function calls and to per-element dynamic type checking.
% Gilles: I don't think it is worth mentionning online learning. They are exceptions in scikit-learn.

% The public API is oriented toward batch processing
% to enable efficient implementation.
% While classification and regression algorithms
% can make predictions for single samples,
% and some algorithms in \sklearn can perform online learning
% (e.g. stochastic gradient descent for linear SVMs and logistic regression,
% an online variant of $k$-means based on \citealt{sculley2010web}),
% these algorithm are really intended to be used on small batches of samples.
% Doing so makes optimal use of NumPy and SciPy
% because they prevent the overhead inherent in Python function calls
% and the language's per-element dynamic type checking.
